Inferring Invariants of Distributed Programs

### 2015-03-04 Doc/approach.tex
timeline

>>>>

Following is the planned milestones and estimated timeline for the project completion.

\begin{description}
  \item[2/10:] Proposal Draft Submission
  \item[3/3:] Proposal Submission
  \item[3/7:] Finalizing the design, Familirization with required tools (Daikon, Go source analysis tools)
  \item[3/14:] Implementation - Go program instrumentation to handle annotations and dumping state
  \item[3/21:] Implementation - Dynamic Forward Analysis for Go programs
  \item[3/28:] Implementation - Vector clocks integration and end-to-end working analysis
  \item[4/4:] Evaluation - Inferring invariants in test programs
  \item[4/7:] Project Presentation
  \item[4/16:] Project Code and Report Submission
\end{description}
